Convective heat transport in stratified atmospheres at low and high Mach number

### 2016-10-13 tex/nusselt_paper.tex
Fixing two typos: epsilon -> \epsilon, Ma^{1/2} -> Ma^{2}

At the constant values of $n_\rho$ and Pr used, the primary control parameters of convection are $\epsilon$
and Ra.  We decompose our atmosphere into the background polytrope ($\ln\rho_{0}, T_{0}$) and the fluctuations
about that background ($\bm{u}, \ln\rho_{1}, T_{1}$).  The scaling of the entropy gradient with $\epsilon$
is reflected in the evolved values of these fluctuations, which follow the scaling of
$T_1/T_0 \propto \rho_{1}/\rho_{0} \propto$ Ma$^{1/2} \propto epsilon$ for low values of $\epsilon$,
as in Fig. \ref{fig:ma_v_eps}.

>>>>

At the constant values of $n_\rho$ and Pr used, the primary control parameters of convection are $\epsilon$
and Ra.  We decompose our atmosphere into the background polytrope ($\ln\rho_{0}, T_{0}$) and the fluctuations
about that background ($\bm{u}, \ln\rho_{1}, T_{1}$).  The scaling of the entropy gradient with $\epsilon$
is reflected in the evolved values of these fluctuations, which follow the scaling of
$T_1/T_0 \propto \rho_{1}/\rho_{0} \propto$ Ma$^{2} \propto \epsilon$ for low values of $\epsilon$,
as in Fig. \ref{fig:ma_v_eps}.
